Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-08-28 code/analysis.Rmd
Removed line that excluded outliers

tidypump <- lapply(seq_along(x), function(i) {
  select(x[[i]], 
         loc = Location, 
         ht = Height,
         t = `time series`,
         mvc = contains("(ppm)")) %>%
    filter(t < 21) %>% #filter a few timepoints outside the normal window 
    mutate(t = (t-min(t)+1)*300, #convert from timestep to seconds
           mvc = as.numeric(mvc), 
           date = as.numeric(names(x)[[i]])) %>%
    filter(mvc < 80) #filter out a few early-timestep anomalies
  }
  )

@@

Let's clean up for the sake of sanity (if you're reading the .pdf, this is unimportant):

rm(fits, pump, pumpdata, tidypump, tidytrap, trap, trapdata, x, estimates, flow, pumpdate, pumpfiles, t_0, t_b, t_f, time, trapdate, trapfiles, poly_fin_integr)

@@

### THE PROBLEM IN A NUTSHELL
Having a greater decay rate for the control run than the dowel run, by an amount greater than the difference in $k_s$ between the two runs, implies a negative $k_c$. This seems unrealistic, or at least very out of step with our operating theory. For the rest of this analysis, I'll do what I slipped into my past code and then forgot about: leave out that control run and estimate its values as the mean of the other controls (it does lie at the mean of their independent vars. so weighting the average seems unnecessary). Not ideal! Maybe we should give this set of parameters another shot? But I don't feel great about cherrypicking experimental results that way either.

>>>>

tidypump <- lapply(seq_along(x), function(i) {
  select(x[[i]], 
         loc = Location, 
         ht = Height,
         t = `time series`,
         mvc = contains("(ppm)")) %>%
    filter(t < 21) %>% #filter a few timepoints outside the normal window 
    mutate(t = (t-min(t)+1)*300, #convert from timestep to seconds
           mvc = as.numeric(mvc), 
           date = as.numeric(names(x)[[i]])) %>%
    filter(!is.na(mvc))
  }
  )

@@

@@

### THE PROBLEM IN A NUTSHELL

Having a greater decay rate for the control run than the dowel run, by an amount greater than the difference in $k_s$ between the two runs, implies a negative $k_c$. This seems unrealistic, or at least very out of step with our operating theory. For the rest of this analysis, I'll do what I slipped into my past code and then forgot about: leave out that control run and estimate its values as the mean of the other controls (it does lie at the mean of their independent vars. so weighting the average seems unnecessary). Not ideal! Maybe we should give this set of parameters another shot? But I don't feel great about cherrypicking experimental results that way either.
